% This file was converted to LaTeX by Writer2LaTeX ver. 1.2
% see http://writer2latex.sourceforge.net for more info
\documentclass[twoside,letterpaper]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{supertabular}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=SYSTEMS AND SOFTWARE REQUIREMENTS SPECIFICATION (SSRS) TEMPLATE, pdfauthor=Clinton Jeffery, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% footnotes configuration
\makeatletter
\renewcommand\thefootnote{\arabic{footnote}}
\makeatother
% Outline numbering
\setcounter{secnumdepth}{3}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\arabic{section}.\arabic{subsection}}
\renewcommand\thesubsubsection{\arabic{section}.\arabic{subsection}.\arabic{subsubsection}}
\renewcommand\thesubparagraph{\arabic{section}.\arabic{subsection}.\arabic{subsubsection}.null{paragraph}.\arabic{subparagraph}}
\makeatletter
\newcommand\arraybslash{\let\\\@arraycr}
\makeatother
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{0.5in}
\setlength\oddsidemargin{1in}
\setlength\evensidemargin{1in}
\setlength\textheight{8.278in}
\setlength\textwidth{6.5in}
\setlength\footskip{0.561in}
\setlength\headheight{0.5in}
\setlength\headsep{0.461in}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertviii{
  \renewcommand\@oddhead{\selectlanguage{english}\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertvii{
  \renewcommand\@oddhead{\selectlanguage{english}\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertvi{
  \renewcommand\@oddhead{\selectlanguage{english}\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill \hfill \hfill  \ \ \ \ \ NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertv{
  \renewcommand\@oddhead{\selectlanguage{english}\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertiv{
  \renewcommand\@oddhead{\selectlanguage{english}\rmfamily\color{black} University of Idaho CS Department Instructional Use\hfill \hfill \hfill \hfill  \ \ \ \ \ \ NOT FOR RELEASE}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{{\foreignlanguage{english}{\textcolor{black}{SSRS Page }}}{\foreignlanguage{english}{\textcolor{black}{\thepage{}}}}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Convertii{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{\@oddhead}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\title{SYSTEMS AND SOFTWARE REQUIREMENTS SPECIFICATION (SSRS) TEMPLATE}
\author{Clinton Jeffery}
\date{2013-09-10}
\begin{document}
\clearpage\setcounter{page}{1}\pagestyle{Standard}


\clearpage{\centering\bfseries
SYSTEMS AND SOFTWARE \ REQUIREMENTS SPECIFICATION (SSRS) FOR 
\par}


\bigskip

{\centering\bfseries
sQuire Collaborative IDE
\par}


\bigskip


\bigskip


\bigskip

\begin{center}
Picture here.
\end{center}

\bigskip


\bigskip

{\centering\bfseries
Version 1.0
\par}

{\centering\bfseries
February 09, 2016
\par}


\bigskip


\bigskip

{\centering\bfseries
Prepared for:
\par}

{\centering\bfseries
CS383-01
\par}


\bigskip


\bigskip

{\centering\bfseries
Prepared by:
\par}

{\centering\bfseries
Domn Werner (wern0096) $\vert$ Robert Carlson (carl7595) $\vert$ Brian Cartwright (cart1189) \\ Max Welch (welc2150) $\vert$ Matthew Daniel (dani2918) $\vert$ Brandon Ratcliff (ratc8795) \\ Joel Doumit (doum6708) $\vert$ Eric Gentile-Quant (gent7104) \\
Team 4 - It Compiled Yesterday (ICY)
\par}

{\centering\bfseries
University of Idaho
\par}

{\centering\bfseries
Moscow, ID \ 83844-1010
\par}

\clearpage{\centering\bfseries
sQuire SSRS
\par}


\bigskip

{\centering\bfseries
RECORD OF CHANGES
\par}


\bigskip

\begin{flushleft}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{0.47685984in}|m{0.6087598in}|m{1.3587599in}|m{0.23375985in}|m{2.0462599in}|m{0.7337598in}|m{0.6330598in}|}
\hline
~

\centering{\selectlanguage{english}\color{black} Change number} &
~

\centering{\selectlanguage{english}\color{black} Date completed} &
~

\centering{\selectlanguage{english}\color{black} Location of change (e.g., page or figure \#)} &
\centering{\selectlanguage{english}\bfseries\color{black} A\newline
M\newline
D} &
~

~

\centering{\selectlanguage{english}\color{black} Brief description of change} &
~

\centering{\selectlanguage{english}\color{black} Approved by (initials)} &
~

\centering\arraybslash{\selectlanguage{english}\color{black} Date Approved}\\\hline
1 & 02/11/16 & Page 1 & M & Updated Team Name & DW & 02/11/16 \\\hline
1 & 02/11/16 & Pages 8-10 & M & Updated Functional Reqs & DW & 02/11/16\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
\end{supertabular}
\end{flushleft}
{\selectlanguage{english}\color{black}
\foreignlanguage{english}{*}\foreignlanguage{english}{\textbf{A}}\foreignlanguage{english}{ - ADDED
\ }\foreignlanguage{english}{\textbf{M}}\foreignlanguage{english}{ - MODIFIED
\ }\foreignlanguage{english}{\textbf{D}}\foreignlanguage{english}{ - DELETED}}

\clearpage{\centering\selectlanguage{english}\bfseries\color{black}
\foreignlanguage{english}{\MakeUppercase{\ sQuire SSRS}}
\par}

{\centering\selectlanguage{english}\bfseries\color{black}
TABLE OF CONTENTS
\par}


\bigskip

{\selectlanguage{english}\bfseries\color{black}
Section\ \ Page}

\setcounter{tocdepth}{9}
\renewcommand\contentsname{}
\tableofcontents

\bigskip

\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertii}
\section[Introduction]{\rmfamily\bfseries Introduction}
\hypertarget{RefHeading15659017292}{}{
{
The sQuire Collaborative IDE is a collaborative IDE software project for CS383-01. The intended audience for this project is Java programmers looking for a more social collaborative experience. A large focus of the program is also to help programmers connect with others who may interested in their projects.}}

\subsection[IDENTIFICATION]{\rmfamily\bfseries IDENTIFICATION}
\hypertarget{RefHeading15859017292}{}
{
The software system being considered for development is referred to as sQuire. \ The customer
providing specifications for the system is Dr. Jeffery and the CS383-01 class. \ The ultimate customer, or end-user, of
the system will be Java programmers. \ This is a new project effort, so the
version under development is version 1.0.}

\subsection[PURPOSE]{\rmfamily\bfseries PURPOSE}
\hypertarget{RefHeading16059017292}{}

{
The purpose of the system under development is to
provide Java programmers with a more social collaborative experience. Instead of individual methods of source control, sQuire will provide an environment where programmers can work together in the same environment and instantly see the effect of others' code. While the system will be used by Java programmers, this document is intended to be read and understood
by UI CS software designers and coders. 
The document will also be vetted or approved by Team 4.}

\subsection[SCOPE]{\rmfamily\bfseries SCOPE}
\hypertarget{RefHeading16259017292}{}{\itshape
This paragraph shall briefly summarize the history of system
development, operation, and maintenance; identify the project
sponsor, acquirer, user, developer, and support agencies; identify
current and planned operating sites; and list other relevant documents.}

{
[ insert your text here ]}

\subsection[DEFINITIONS, ACRONYMS, AND ABBREVIATIONS]{\rmfamily\bfseries
DEFINITIONS, ACRONYMS, AND ABBREVIATIONS}
\hypertarget{RefHeading16459017292}{}{\itshape
This section shall list and define all special terms, acronyms
and abbreviations used throughout this document. A
tabular form is preferable, but not mandatory.}


\bigskip

\begin{flushleft}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{1.3587599in}|m{5.00806in}|}
\hline
\centering{\bfseries Term or Acronym} &
\centering\arraybslash{\bfseries Definition}\\\hline
{Alpha test} &
{Limited release(s) to selected, outside testers}\\\hline
{Beta test} &
{Limited release(s) to cooperating customers wanting early access to developing
systems}\\\hline
{Final test} &
{aka, Acceptance test, release of full functionality to customer for
approval}\\\hline
{DFD} &
{Data Flow Diagram}\\\hline
{SDD} &
{Software Design Document, aka SDS, Software Design Specification}\\\hline
{SRS} &
{Software Requirements Specification}\\\hline
{SSRS} &
{System and Software Requirements Specification}\\\hline
{IDE} &
Integrated Development Environment\\\hline
~
 &
~
\\\hline
~
 &
~
\\\hline
~
 &
~
\\\hline
\end{supertabular}
\end{flushleft}
\subsection[REFERENCES]{\rmfamily\bfseries REFERENCES}
\hypertarget{RefHeading16659017292}{}{\itshape
This section shall list full bibliographic citations of all
documents referenced in this report. This section shall also
identify the source for all materials not available in printed
form (e.g., web-based information) and list the
complete URL along with owner, author, posting date, and date last visited.}

{
[ insert your citations here ]}

\subsection[OVERVIEW AND RESTRICTIONS]{\rmfamily\bfseries OVERVIEW AND
RESTRICTIONS}
\hypertarget{RefHeading16859017292}{}{\itshape
This paragraph shall describe the organization of this document
and shall describe any security or privacy
considerations associated with its use.}

{
This document is for limited release only to UI CS personnel working
on the project and [ state others who will receive
the document ].}


\bigskip

{
Section 2 of this document describes the system under development
from a holistic point of view. Functions,
characteristics, constraints, assumptions, dependencies, and overall
requirements are defined from the system-level perspective.}


\bigskip

{
Section 3 of this document describes the specific requirements of
the system being developed. Interfaces, features, and specific
requirements are enumerated and described to a degree sufficient
for a knowledgeable designer or coder to
begin crafting an architectural solution to the proposed system.}


\bigskip

{
Section 4 provides the requirements traceability information for the
project. Each feature of the system is indexed by
the SSRS requirement number and linked to its SDD and test references.}


\bigskip

{
Sections 5 and up are appendices including original information and
communications used to create this document.}

\clearpage\section[OVERALL DESCRIPTION]{\rmfamily\bfseries OVERALL DESCRIPTION}
\hypertarget{RefHeading17059017292}{}{
{The sQuire project is an answer to the lack of real-time collaborative programming experiences. By bringing programmers together in a more social environment, this program aims to improve collaboration between programmers in a much more fast paced and agile methodology. Furthermore, for programmers who seek others to help with their projects, sQuire aims to provide a simple social platform for engaging with other programmers and start working on a project together.}}

\subsection[PRODUCT PERSPECTIVE]{\rmfamily\bfseries PRODUCT PERSPECTIVE}
\hypertarget{RefHeading17259017292}{}{
\foreignlanguage{english}{This program will either be a standalone executable with many linked DLLs or a web application that can run on most modern web-browsers with internet access.}}

{\selectlanguage{english}\color{black}
}

\subsection[PRODUCT FUNCTIONS]{\rmfamily\bfseries PRODUCT FUNCTIONS}
\hypertarget{RefHeading17459017292}{}{\itshape
This subsection of the document should provide a summary of the major
functions that the software will perform. For the sake of clarity, the
functions should be organized in a way that makes the list of
functions understandable to the customer or to anyone else reading
the document for the first time. Textual or graphical methods can
be used to show the different functions and their relationships.
Such a diagram is not intended to show a design of a product,
but simply shows the logical relationships among variables.}

[ insert your text here ]

\subsection[USER CHARACTERISTICS]{\rmfamily\bfseries USER CHARACTERISTICS}
\hypertarget{RefHeading17659017292}{}{\itshape
This subsection of the document should describe those general
characteristics of the intended users of the product including
educational level, experience, and technical expertise. It
should not be used to state specific
requirements, but rather should provide the reasons why certain
specific requirements are later specified in
Section 3 of this document.}

[ insert your text here ]

\subsection[CONSTRAINTS]{\rmfamily\bfseries CONSTRAINTS}
\hypertarget{RefHeading17859017292}{}{\itshape
This subsection of the document should provide a general description
of any other items that will limit the developer's options. These
include: a) Regulatory policies; b) Hardware limitations (e.g.,
signal timing requirements); c) Interfaces to other applications;
d) Parallel operation; e) Audit functions; f) Control functions;
g) Higher-order language requirements; h) Signal handshake
protocols; i) Reliability requirements; j) Criticality of the
application; k) Safety and security considerations.}

[ insert your text here ]

\subsection[ASSUMPTIONS AND DEPENDENCIES]{\rmfamily\bfseries ASSUMPTIONS AND
DEPENDENCIES}
\hypertarget{RefHeading18059017292}{}{\itshape
This subsection of the document should list each of the factors
that affect the requirements stated in the document. These factors
are not design constraints on the system and/or software but are,
rather, any changes to them that can affect the requirements in the
document. For example, an assumption may be that a specific
operating system will be available on the hardware designated for
the software product. If, in fact, the operating system is not available,
the document would then have to change accordingly.}

[ insert your text here ]

\subsection[SYSTEM LEVEL (NON{}-FUNCTIONAL) REQUIREMENTS]{\rmfamily\bfseries
SYSTEM LEVEL (NON-FUNCTIONAL) REQUIREMENTS}
\hypertarget{RefHeading18259017292}{}{\itshape
This subsection of the document should identify system level (whole,
not functional) requirements that impact the
construction, operation, packaging and delivery of the system and software.}

\subsubsection[Site dependencies]{\rmfamily\bfseries Site dependencies}
\hypertarget{RefHeading18459017292}{}{
{\textit{This paragraph shall specify site-dependent operational
parameters and needs (such as parameters indicating operation-dependent
targeting constants or data recording).}}
{\textit{The requirements shall include, as applicable, number of
each type of equipment, type, size, capacity, and other required
characteristics of processors, memory, input/output devices, auxiliary
storage, communications/ network equipment, and other required
equipment or software that must be used by, or incorporated into,
the system. Examples include operating systems, database management
systems, communications/network software, utility software, input
and equipment simulators, test software, and manufacturing software. The
correct nomenclature, version, and documentation references of each
such device or software item shall be provided.}}}

\begin{enumerate}
  \item Central SQL Server
  \item Host-side Project Server
  \item Collaborator-side Client
\end{enumerate}

The Central server stores user credentials, project descriptions, and user profile and achievement data. 

Requirements for Central SQL Server
\begin{enumerate}
  \item Host with high uptime percentage
  \item SQL capable
  \item E-mail capable for password resets
  \item Fast enough connection to prevent login timeout, even while handling multiple requests
  \item Prefer host with multiple backups
\end{enumerate}

The Host-side server stores the project files, project access list, hosts the editing environment, runs chat channels, and serves files to collaborators for compiling.

Requirements for Host-side Server
\begin{enumerate}
  \item Java Capable (http://java.com/en/download/help/sysreq.xml)
  \item SQL Capable (WAMP/LAMP)
  \item 4 GB RAM
  \item Hard drive space for server + project files
\end{enumerate}

The client side application connects to the host server, renders GUI elements, stores connection profiles, stores server files, and compiles the project.

Requirements for Collaborator-side Client
\begin{enumerate}
  \item Java Capable (http://java.com/en/download/help/sysreq.xml)
  \item Project specified Java installed
  \item 2 GB RAM
  \item Hard drive space for project files
\end{enumerate}

\subsubsection[Safety, security and privacy requirements]{\rmfamily\bfseries
Safety, security and privacy requirements}
\hypertarget{RefHeading18659017292}{}{\itshape
This paragraph shall specify the system requirements, if any,
concerned with maintaining safety, security and privacy.
These requirements shall include, as applicable, the safety,
security and privacy environment in which the system must
operate, the type and degree of security or privacy to be
provided, and the criteria that must be met for
safety/security/privacy certification and/or accreditation.}

The collaborative nature of sQuire includes several concerns for security and privacy. The program will include in the license agreement the following stipulations:
\begin{enumerate}
  \item sQuire is a free development environment, and may be used for commercial purposes
  \item No guarantee of code confidentiality is implied by use of sQuire
  \item Clients assume the risk of downloading, compiling, and running project files
  \item Email addresses are visible as part of a user profile
  \item Host assume the risk of allowing peers to connect to their server
\end{enumerate}

However, the program will provide the following minimum features to address security and privacy concerns:
\begin{enumerate}
  \item All SQL servers will include input sanitization and appropriate anti-injection safeguards
  \item Project hosts may turn off guest access to their project
  \item Uploads for assets will be limited to folders within the project directory
  \item Visibility to host file structure will be limited to project folders only
\end{enumerate}

\subsubsection[Performance requirements]{\rmfamily\bfseries Performance
requirements}
\hypertarget{RefHeading18859017292}{}{\itshape
This paragraph should specify both the static and the dynamic
numerical performance requirements placed on the software
or on human interaction as a whole. Static numerical requirements
may include the following: a) The number of terminals to be supported;
b) The number of simultaneous users to be supported; c) Amount and
type of information to be handled. Dynamic numerical requirements
may include, for example, the numbers of transactions and tasks and the
amount of data to be processed within certain time periods for both
normal and peak workload conditions. All of these requirements should
be stated in measurable terms. For example, ``95\% of the transactions
shall be processed in less than 1msec.''}

\begin{enumerate}
  \item Up to 33 concurrent connections will be supported
  \item Edits will be visible to all connected collaborators within 10 seconds
  \item Login and server connections will report success or failure within 45 seconds
\end{enumerate}

\subsubsection[System and software quality]{\rmfamily\bfseries System and software
quality}
\hypertarget{RefHeading19059017292}{}{\itshape
This paragraph shall specify the requirements, if any, concerned
with hardware and software quality factors identified in the contract.
Examples include quantitative requirements regarding the system's
functionality (the ability to perform all required functions),
reliability (the ability to perform with correct, consistent
results), maintainability (the ability to be easily corrected),
availability (the ability to be accessed and operated when needed),
flexibility (the ability to be easily adapted to changing requirements),
portability (the ability to be easily modified for a new environment),
reusability (the ability to be used in multiple applications),
testability (the ability to be easily and thoroughly tested),
usability (the ability to be easily learned and used), and other attributes.}

Adaptability
\begin{enumerate}
  \item The program will allow selection of different compiling programs and command line arguments.
  \item The program will allow importing of files of key words to allow other development languages to be used.
\end{enumerate}

\subsubsection[Packaging and delivery requirements]{\rmfamily\bfseries
Packaging and delivery requirements}
\hypertarget{RefHeading19259017292}{}{\itshape
This paragraph shall specify the requirements, if any, for packaging,
labeling, handling and delivery of the system
being developed to the customer.}

The executable system and all associated documentation (i.e., SSRS,
SDD, code listing, test plan (data and results), and user manual) will
be delivered to the customer on CD's and/or via email, as specified by
the customer at time of delivery. Although document ``drops'' will
occur throughout the system development process, the final, edited
version of the above documents will accompany the final, accepted
version of the executable system.

\subsubsection[Personnel{}-related requirements]{\rmfamily\bfseries
Personnel-related requirements}
\hypertarget{RefHeading19459017292}{}{
{\textit{This paragraph shall specify the system requirements,
if any, included to accommodate
the number, skill levels, duty cycles, training needs, or other information about the personnel who will use or support
the system under development. These requirements shall include, as applicable, considerations for the capabilities
and limitations of humans; foreseeable human errors under both normal and extreme conditions; and specific areas where
the effects of human error would be particularly serious. \ Examples include requirements for color and duration of
error messages, physical placement of critical indicators or keys, and use of auditory
signals.}}\foreignlanguage{english}{ }}

{\selectlanguage{english}\color{black}
The system under development has no special personnel-related characteristics. }

\subsubsection[Training{}-related requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black} Training-related
requirements}
\hypertarget{RefHeading19659017292}{}{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\textit{This paragraph shall specify the system requirements, if any, pertaining to training.
\ Examples include training software, tutorials, or help information to be included in the
system.}}\foreignlanguage{english}{ \ \ }}

{\selectlanguage{english}\color{black}
No training materials or expectations are tied to this project other than the limited help screens built into the
software and the accompanying user manual.}

\subsubsection[Logistics{}-related requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black}
Logistics-related requirements}
\hypertarget{RefHeading19859017292}{}{\selectlanguage{english}\itshape\color{black}
This paragraph shall specify the system requirements, if any, concerned with logistics considerations. These
considerations may include: system maintenance, software support, system transportation modes, supply-system
requirements, impact on existing facilities, and impact on existing
equipment.
}

{[ Insert a description of the minimum hardware requirements and OS and application software dependencies here ]}


\subsubsection[Other requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black} Other requirements}
\hypertarget{RefHeading20059017292}{}{\selectlanguage{english}\itshape\color{black}
This paragraph shall specify additional system level requirements, if any, not covered in the previous paragraphs.}

{\selectlanguage{english}\color{black}
[ insert your text here ]}

\subsubsection[Precedence and criticality of requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black}
Precedence and criticality of requirements}
\hypertarget{RefHeading20259017292}{}{\selectlanguage{english}\itshape\color{black}
This paragraph shall specify, if applicable, the order of precedence, criticality, or assigned weights indicating the
relative importance of the requirements in this specification. \ Examples include identifying those requirements deemed
critical to safety, to security, or to privacy for purposes of singling them out for special treatment. \ If all
requirements have equal weight, this paragraph shall so state. }

{\selectlanguage{english}\color{black}
[ insert your text here ]}

\clearpage\section[SPECIFIC REQUIREMENTS]{\selectlanguage{english}\rmfamily\bfseries\color{black} SPECIFIC REQUIREMENTS}
\hypertarget{RefHeading20459017292}{}{\selectlanguage{english}\color{black}
	
\subsection{Functional Requirements}

\subsubsection{Project Browsing}

These requirements involve the ability for users to find and learn about projects that they may wish to contribute to. Users shall be able to:

\begin{enumerate}
	\item See a list of open projects.
	\item Filter or search projects.
	\item View more information about a specific project.
	\item Upvote and downvote projects.
	\item Comment on projects and interact with its contributors.
	\item Request to join a specific project.
\end{enumerate}

\subsubsection{Authentication}

These requirements involve the ability for users to have individual accounts and the security that comes from that. Users shall be able to:

\begin{enumerate}
	\item Register for a sQuire user account.
	\item Log in to their user account.
	\item Log out of their user account.
	\item Reset their password via email.
\end{enumerate}

\subsubsection{Communication}

These requirements involve the ability for users to be able to communicate with other users. Users shall be able to:

\begin{enumerate}
	\item Open and close project chat.
	\item Write to project chat.
	\item Read from project chat.
	\item Message a user by their name.
	\item Leave a comment in a file.
\end{enumerate}

\subsubsection{File Management}

These requirements involve the ability for users to manage the files that compose a project. Users shall be able able to:

\begin{enumerate}
	\item Open one or more files.
	\item Close one or more files.
	\item Delete one or more files.
	\item Download one or more files.
	\item Add a new file to the project.
	\item Add an existing file to the project.
	\item Save one or more files.
\end{enumerate}

\subsubsection{File Editing}

These requirements involve the collaborative editor part of sQuire. Users shall be able to:

\begin{enumerate}
	\item Enable or disable line numbers.
	\item Enable or disable viewing reference counts above each line.
	\item Enable or disable viewing date of last edit above each line.
	\item Enable or disable view author of each line.
	\item Comment/Uncomment a selected section code.
	\item Format the document to adhere to code style.
	\item Find/Replace specified text.
	\item View text highlighted by other users.
	\item Type text and have the system apply syntax coloring for Java files and display errors.
	\item View other users' carets as they type.
\end{enumerate}

\subsubsection{Project Management}

These requirements involve the management of entire projects. Users shall be able to:

\begin{enumerate}
	\item Compile a project.
	\item Execute a compiled project.
	\item Create a new project.
	\item Delete a project.
	\item Open a project.
	\item Close a project.
	\item Invite a user to a project.
	\item Join a project.
	\item Leave a project.
\end{enumerate}

\subsubsection{Project Member Management}

These requirements involve project admins managing their members. Admins shall be able to:

\begin{enumerate}
	\item Invite users to a project.
	\item Change user permissions to a project.
	\item Remove users from a project.
	\item Block a user from a project.
\end{enumerate}

\subsubsection{User Preferences}

These requirements involve managing user preferences. Users shall be able to:

\begin{enumerate}
	\item Update their username.
	\item Update their password.
	\item Update their email address.
	\item Update their biography.
	\item Update their display name.
	\item Enable receiving email updates.
	\item Enable receiving messages from any user.
	\item Display their email address to selected groups.
	\item Change program colors.
\end{enumerate}

}

\subsection[EXTERNAL INTERFACE REQUIREMENTS]{\selectlanguage{english}\rmfamily\bfseries\color{black} EXTERNAL INTERFACE
REQUIREMENTS}
\hypertarget{RefHeading20659017292}{}{\selectlanguage{english}\itshape\color{black}
This subsection should be a detailed description of all inputs into and outputs from the software system. \ It should
complement the constraints and dependencies defined in earlier sections, but not repeat that information. \ Hardware,
software, user, and other communication interfaces need to be specified. \ Use the four subsections listed below or the
table on the next page, or some combination of both.}

\subsubsection[Hardware Interfaces]{\selectlanguage{english}\rmfamily\bfseries\color{black} Hardware Interfaces}
\hypertarget{RefHeading20859017292}{}{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\ [ insert your text here ]}}

\subsubsection[Software Interfaces]{\selectlanguage{english}\rmfamily\bfseries\color{black} Software Interfaces}
\hypertarget{RefHeading21059017292}{}{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\ [ insert your text here ]}}

\subsubsection[User Interfaces]{\selectlanguage{english}\rmfamily\bfseries\color{black} User Interfaces}
\hypertarget{RefHeading21259017292}{}{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\ [ insert your text here ]}}

\subsubsection[Other Communication Interfaces]{\selectlanguage{english}\rmfamily\bfseries\color{black} Other
Communication Interfaces}
\hypertarget{RefHeading21459017292}{}{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\ [ insert your text here ]}}


\bigskip


\bigskip

\bigskip
\clearpage\setcounter{page}{1}\pagestyle{Convertiv}

\bigskip

\begin{flushleft}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{0.7337598in}|m{1.4212599in}|m{2.7337599in}|m{1.0462599in}|m{1.4837599in}|m{1.1087599in}m{-0.054440156in}|}
\multicolumn{6}{m{8.92126in}}{{\centering\selectlanguage{english}\bfseries\color{black} External Interface
Requirements\par}

~

\centering{\selectlanguage{english}\bfseries\color{black} Hardware Interfaces}} &
\multicolumn{1}{m{-0.054440156in}}{~
}\\\hline
\centering{\selectlanguage{english}\bfseries\color{black} Name} &
\centering{\selectlanguage{english}\bfseries\color{black} Source/Destination} &
\centering{\selectlanguage{english}\bfseries\color{black} Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Type/range} &
\centering{\selectlanguage{english}\bfseries\color{black} Dependencies} &
\multicolumn{2}{m{1.1330599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Formats}}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
\multicolumn{6}{m{8.92126in}}{~

\centering{\selectlanguage{english}\bfseries\color{black} Software Interfaces}} &
\multicolumn{1}{m{-0.054440156in}}{~
}\\\hline
\centering{\selectlanguage{english}\bfseries\color{black} Name} &
\centering{\selectlanguage{english}\bfseries\color{black} Source/Destination} &
\centering{\selectlanguage{english}\bfseries\color{black} Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Type/range} &
\centering{\selectlanguage{english}\bfseries\color{black} Dependencies} &
\multicolumn{2}{m{1.1330599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Formats}}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
\multicolumn{6}{m{8.92126in}}{~

\centering{\selectlanguage{english}\bfseries\color{black} User Interfaces}} &
\multicolumn{1}{m{-0.054440156in}}{~
}\\\hline
\centering{\selectlanguage{english}\bfseries\color{black} Name} &
\centering{\selectlanguage{english}\bfseries\color{black} Source/Destination} &
\centering{\selectlanguage{english}\bfseries\color{black} Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Type/range} &
\centering{\selectlanguage{english}\bfseries\color{black} Dependencies} &
\multicolumn{2}{m{1.1330599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Formats}}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
\multicolumn{6}{m{8.92126in}}{~

\centering{\selectlanguage{english}\bfseries\color{black} Other Communication Interfaces}} &
\multicolumn{1}{m{-0.054440156in}}{~
}\\\hline
\centering{\selectlanguage{english}\bfseries\color{black} Name} &
\centering{\selectlanguage{english}\bfseries\color{black} Source/Destination} &
\centering{\selectlanguage{english}\bfseries\color{black} Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Type/range} &
\centering{\selectlanguage{english}\bfseries\color{black} Dependencies} &
\multicolumn{2}{m{1.1330599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Formats}}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
~
 &
~
 &
~
 &
~
 &
~
 &
\multicolumn{2}{m{1.1330599in}|}{~
}\\\hline
\end{supertabular}
\end{flushleft}
\clearpage\setcounter{page}{1}\pagestyle{Convertv}
\subsection[SYSTEM FEATURES]{\selectlanguage{english}\rmfamily\bfseries\color{black} SYSTEM FEATURES}
\hypertarget{RefHeading21659017292}{}{\selectlanguage{english}\itshape\color{black}
Functional requirements should define the fundamental actions (i.e., features) \ that must take place in the software in
accepting and processing the inputs and in processing and generating the outputs. These requirements are given in the
form of \textbf{Use Cases} where possible, denoting a concrete use (discrete user-performable task) of the system. Use
case diagrams are followed by use case descriptions, followed by any non-task features. Non-task features are generally
listed as ``shall'' statements starting with ``The system shall{\dots}'' \ These include: a) Validity checks on the
inputs; b) Exact sequence of operations; c) Responses to abnormal situations, including error detection, handling and
recovery; d) Parameter specification and usage; e) Relationship of outputs to inputs, including formulas for input to
output conversion. \newline
\newline
It may be appropriate to partition the functional requirements into sub functions or subprocesses, but that
decomposition (here) does not imply that the software design will also be partitioned that way. \ You should repeat
subsections 3.3.i for every specified feature defined for the system or software.}

\subsubsection[\ Use Case Diagrams]{\foreignlanguage{english}{\ Use Case Diagrams}}
\hypertarget{RefHeading21859017292}{}{\selectlanguage{english}\color{black}
[insert 1+ use case diagrams here]}

\subsubsection[System feature 1: [ insert feature name here {]}]{\selectlanguage{english}\rmfamily\bfseries\color{black}
System feature 1: [ insert feature name here ]}
\hypertarget{RefHeading22059017292}{}
\bigskip

{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\textit{For each feature, you should either provide a Use Case Description
}}\foreignlanguage{english}{\textbf{\textit{or}}}\foreignlanguage{english}{\textit{ a Non-task feature description,
whichever is more appropriate.}}}


\bigskip

\begin{flushleft}
\tablefirsthead{}
\tablehead{}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{|m{3.17056in}|m{3.1740599in}|}
\hline
{\selectlanguage{english}\bfseries\color{black} Use Case Description} &
\paragraph[Non{}-task feature description]{\selectlanguage{english}\rmfamily\bfseries\color{black} Non-task feature
description}
\hypertarget{RefHeading22259017292}{}\\\hline
{\selectlanguage{english}\bfseries\color{black} Name}

{\selectlanguage{english}\color{black} Actors}

{\selectlanguage{english}\color{black} Goals}

{\selectlanguage{english}\color{black} Preconditions}

{\selectlanguage{english}\bfseries\color{black} Summary}

{\selectlanguage{english}\color{black} Related use cases}

{\selectlanguage{english}\bfseries\color{black} Steps}

{\selectlanguage{english}\color{black} \ \ \ 1. ...}

{\selectlanguage{english}\color{black} \ \ \ 2. ...}

{\selectlanguage{english}\color{black} Alternatives}

{\selectlanguage{english}\color{black} Postconditions}

~
 &
\paragraph[\ Introduction/Purpose]{\foreignlanguage{english}{\ Introduction/Purpose}}
\hypertarget{RefHeading22459017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\paragraph[Input/Output sequence]{\selectlanguage{english}\rmfamily\bfseries\color{black} Input/Output sequence}
\hypertarget{RefHeading22659017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\paragraph[Design constraints]{\selectlanguage{english}\rmfamily\bfseries\color{black} Design constraints}
\hypertarget{RefHeading22859017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\paragraph[Performance requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black} Performance requirements}
\hypertarget{RefHeading23059017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\paragraph[Detailed functional requirements]{\selectlanguage{english}\rmfamily\bfseries\color{black} Detailed functional
requirements}
\hypertarget{RefHeading23259017292}{}\subparagraph[Functional requirement 1.1]{Functional requirement 1.1}
\hypertarget{RefHeading23459017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\subparagraph[Functional requirement 1.2]{Functional requirement 1.2}
\hypertarget{RefHeading23659017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}

\paragraph[]{\selectlanguage{english}\rmfamily\bfseries\color{black} }
\subparagraph[{\dots}]{{\dots}}
\hypertarget{RefHeading23859017292}{}\subparagraph[Functional requirement 1.[n{]}]{Functional requirement 1.[n]}
\hypertarget{RefHeading24059017292}{}{\selectlanguage{english}\color{black} [ insert your text here ]}\\\hline
\end{supertabular}
\end{flushleft}

\bigskip

\subsubsection[System feature 2: [ insert feature name here {]}]{\selectlanguage{english}\rmfamily\bfseries\color{black}
System feature 2: [ insert feature name here ]}
\hypertarget{RefHeading24259017292}{}\paragraph[Write another feature description, as either a use case or a non{}-task
feature description]{\selectlanguage{english}\rmfamily\itshape\color{black} Write another feature description, as
either a use case or a non-task feature description}
\subparagraph[{\dots} do as many as necessary, probably a lot]{{\dots} do as many as necessary, probably a lot}
\hypertarget{RefHeading26259017292}{}\subsubsection[System feature [m{]}: [ insert feature name here
{]}]{\selectlanguage{english}\rmfamily\bfseries\color{black} System feature [m]: [ insert feature name here ]}
\hypertarget{RefHeading26459017292}{}\paragraph[Write a final feature description, as either a use case or a non{}-task
feature description]{\selectlanguage{english}\rmfamily\itshape\color{black} Write a final feature description, as
either a use case or a non-task feature description}
\subparagraph[]{\selectlanguage{english}\rmfamily\color{black} }
\clearpage\setcounter{page}{1}\pagestyle{Convertvi}
\section[REQUIREMENTS TRACEABILITY]{\selectlanguage{english}\rmfamily\bfseries\color{black} REQUIREMENTS TRACEABILITY}
\hypertarget{RefHeading28459017292}{}{\selectlanguage{english}\itshape\color{black}
This section shall contain traceability information from each system requirement in this specification to the system (or
subsystem, if applicable) requirements it addresses. \ A tabular form is preferred, but not mandatory.}


\bigskip

\begin{flushleft}
\tablefirsthead{\hline
\multicolumn{1}{|m{0.9212598in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Feature Name}} &
\centering{\selectlanguage{english}\bfseries\color{black} Req No.} &
\centering{\selectlanguage{english}\bfseries\color{black} Requirement Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Priority} &
\centering{\selectlanguage{english}\bfseries\color{black} SDD} &
\multicolumn{2}{m{1.2872598in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Alpha Release}} &
\multicolumn{2}{m{1.3587599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Beta Release}} &
\multicolumn{2}{m{1.3795599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Final Test}}\\\hline
 &
 &
 &
 &
 &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Res.} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Res.} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
{\selectlanguage{english}\bfseries\color{black} Test Res.}\\}
\tablehead{\hline
\multicolumn{1}{|m{0.9212598in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Feature Name}} &
\centering{\selectlanguage{english}\bfseries\color{black} Req No.} &
\centering{\selectlanguage{english}\bfseries\color{black} Requirement Description} &
\centering{\selectlanguage{english}\bfseries\color{black} Priority} &
\centering{\selectlanguage{english}\bfseries\color{black} SDD} &
\multicolumn{2}{m{1.2872598in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Alpha Release}} &
\multicolumn{2}{m{1.3587599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Beta Release}} &
\multicolumn{2}{m{1.3795599in}|}{\centering{\selectlanguage{english}\bfseries\color{black} Final Test}}\\\hline
 &
 &
 &
 &
 &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Res.} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Res.} &
\centering{\selectlanguage{english}\bfseries\color{black} Test Case(s)} &
{\selectlanguage{english}\bfseries\color{black} Test Res.}\\}
\tabletail{}
\tablelasttail{}
\begin{supertabular}{m{0.9212598in}|m{0.42125985in}|m{1.9212599in}|m{0.39275986in}|m{0.7587598in}|m{0.6622598in}|m{0.5462598in}|m{0.6712598in}|m{0.6087598in}|m{0.6712598in}|m{0.6295598in}|}
\hhline{~~~~~------}
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} 1.1} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
 &
\centering{\selectlanguage{english}\color{black} 1.2} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} {\dots}} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} 1.[n]} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} 2.1} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
 &
\centering{\selectlanguage{english}\color{black} 2.2} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} {\dots}} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} 2.[n]} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} 3.1} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
 &
\centering{\selectlanguage{english}\color{black} 3.2} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} {\dots}} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
 &
\centering{\selectlanguage{english}\color{black} 3.[n]} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
\multicolumn{1}{|m{0.9212598in}|}{{\selectlanguage{english}\color{black} {\dots}}} &
\centering{\selectlanguage{english}\color{black} {\dots}} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} [m].1} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
 &
\centering{\selectlanguage{english}\color{black} [m].2} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hhline{~----------}
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} {\dots}} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
\multicolumn{1}{|m{0.9212598in}|}{~
} &
\centering{\selectlanguage{english}\color{black} [m.n]} &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
 &
~
\\\hline
\end{supertabular}
\end{flushleft}
{\selectlanguage{english}\color{black}
Priorities are: \textbf{M}andatory, \textbf{L}ow, \textbf{H}igh}

{\selectlanguage{english}\color{black}
SDD link is version and page number or function name.}

{\selectlanguage{english}\color{black}
Test cases and results are file names and \textbf{P}ass/\textbf{F}ail or \% passing.}

\clearpage\setcounter{page}{1}\pagestyle{Convertvii}
\section[APPENDIX A. \ [insert name here{]}]{\selectlanguage{english}\rmfamily\bfseries\color{black} APPENDIX A.
\ [insert name here]}
\hypertarget{RefHeading28659017292}{}
\bigskip

{\selectlanguage{english}\itshape\color{black}
Include copies of specifications, mockups, prototypes, etc. supplied or derived from the customer. \ Appendices are
labeled A, B, {\dots}n. \ \ Reference each appendix as appropriate in the text of the document. }

{\selectlanguage{english}\color{black}
\foreignlanguage{english}{\ [ insert appendix A here ]}}

\clearpage\setcounter{page}{1}\pagestyle{Convertviii}
\section[APPENDIX B. \ [insert name here{]}]{\selectlanguage{english}\rmfamily\bfseries\color{black} APPENDIX B.
\ [insert name here]}
\hypertarget{RefHeading28859017292}{}
\bigskip

{\selectlanguage{english}\color{black}
[ insert appendix B here ]}


\bigskip
\end{document}
